Modeling site-specific amino-acid preferences deepens phylogenetic estimates of viral divergence

### 2018-04-16 manuscript/manuscript.tex
_MBE_ submitted version

% added by SKH
\usepackage{lineno}
\linenumbers

@@

\title{Modeling site-specific amino-acid preferences deepens phylogenetic divergence estimates for viral proteins}

@@

\subsection*{Software versions and computer code}
All code used for the analyses in this paper is available at \url{https://github.com/jbloomlab/divergence_timing_manuscript}.
The external computer programs that we used were
\begin{itemize} 
\item \texttt{phydms}~\citep{hilton2017phydms} version 2.2.2 (available at \url{github.com/jbloomlab/phydms}) to fit the ExpCM and GY94 models.
\item \texttt{pyvolve}~\citep{spielman2015pyvolve} version 0.8.7 (available at \url{https://github.com/sjspielman/pyvolve}) to simulate the sequences.
\item \texttt{PhyloBayes-MPI}~\citep{rodrigue2014site} version 1.8 (available at \url{https://github.com/bayesiancook/pbmpi}) to fit the pbMutSel model. 
\item \texttt{RAxML}~\citep{stamatakis2006raxml} version 8.2.11 (available at \url{https://github.com/stamatak/standard-RAxML}) to infer tree topology.
\item We used \texttt{ggplot2}~\citep{wickham2016ggplot2}, \texttt{ggtree}~\citep{yu2017ggtree}, and \texttt{ggseqlogo}~\citep{wagih2017ggseqlogo} for visualization of the results.
\item \texttt{snakemake}~\citep{koster2012snakemake} version 3.11.2 (available at \url{https://snakemake.readthedocs.io/en/stable/}) to run the pipelines.
\end{itemize}

@@

\clearpage 
\bibliographystyle{mbe}
\bibliography{references.bib}

\newpage
\section*{Supplemental Information}

>>>>

% added by SKH
\usepackage{lineno}
%\linenumbers

@@

\title{Modeling site-specific amino-acid preferences deepens phylogenetic estimates of viral divergence}

@@

\subsection*{Software versions and computer code}
All code used for the analyses in this paper is available at \url{https://github.com/jbloomlab/divergence_timing_manuscript}.
External computer programs used were \texttt{phydms}~\citep{hilton2017phydms} version 2.2.2, \texttt{pyvolve}~\citep{spielman2015pyvolve} version 0.8.7, \texttt{PhyloBayes-MPI}~\citep{rodrigue2014site} version 1.8, \texttt{RAxML}~\citep{stamatakis2006raxml} version 8.2.11 (available at \url{https://github.com/stamatak/standard-RAxML}), \texttt{ggplot2}~\citep{wickham2016ggplot2}, \texttt{ggtree}~\citep{yu2017ggtree}, \texttt{ggseqlogo}~\citep{wagih2017ggseqlogo}, and \texttt{snakemake}~\citep{koster2012snakemake} version 3.11.2.

@@

\clearpage 
\bibliographystyle{mbe}
{\small
\bibliography{references.bib}
}

\newpage
\setcounter{page}{1}
\renewcommand{\thepage}{S\arabic{page}}
\section*{Supplemental Information}
